Compilation With Program Synthesis

### 2023-09-07 new-paper/examples.tex
update table description

Figure~\ref{fig:pika-2-examples} is a table of \Pika{} 2 examples together with the number of functions they have (not including \synth) and whether or not they use \synth. These functions were tested using the unit testing framework built into \Pika{} 2.

>>>>

Figure~\ref{fig:pika-2-examples} is a table of \Pika{} 2 examples together with the number of functions they have (not including \synth). These functions were tested using the unit testing framework built into \Pika{} 2.
